---
title: "data-access"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Packages
```{r}
library(readr)
library(contentid)
library(pins)
```


# Demo of the pins package

```{r}
delta_sites_edi <- 'https://portal.edirepository.org/nis/dataviewer?packageid=edi.233.2&entityid=6a82451e84be1fe82c9821f30ffc2d7d'
delta_sites_edi_pin<-pins::pin(delta_sites_edi)
delta_sites <- readr::read_csv(delta_sites_edi_pin, show_col_types = FALSE)
head(delta_sites)
```

But pins doesn't track versioning of datasets. It only points to a URL
You can use option verify=TRUE, in which case it downloads the dataset and compares to the version on disk. But this requires it to re-download every time. 

DOIs are a reference to a data set, but not to single data files. DOIs link to landing page for dataset, not to the locations of the single files. 

# Resolving data with contentID
```{r}
library(contentid)
delta_catch_edi <- 'https://portal.edirepository.org/nis/dataviewer?packageid=edi.233.2&entityid=015e494911cf35c90089ced5a3127334'
delta_catch_dataone <- 'https://cn.dataone.org/cn/v2/resolve/https%3A%2F%2Fpasta.lternet.edu%2Fpackage%2Fdata%2Feml%2Fedi%2F233%2F2%2F015e494911cf35c90089ced5a3127334'
delta_taxa_edi <- 'https://portal.edirepository.org/nis/dataviewer?packageid=edi.233.2&entityid=0532048e856d4bd07deea11583b893dd'
delta_effort_edi <- 'https://portal.edirepository.org/nis/dataviewer?packageid=edi.233.2&entityid=ace1ef25f940866865d24109b7250955'

# Store edi version of catch table with content identifier
delta_catch_id<-store(delta_catch_edi)

# Check that EDI version is the same as dataone version
delta_catch_id_dataone<-store(delta_catch_dataone)
delta_catch_id==delta_catch_id_dataone

# Find path on local machine to this file
retrieve(delta_catch_id)

# read in the file
delta_catch <- read_csv(retrieve(delta_catch_id))

# Or can just use resolve function instead of retrieve
delta_catch_file<-resolve(delta_catch_id, store=TRUE)
delta_catch <- read_csv(delta_catch_file)
```

